\bf Is this normal? A new projection pursuit index to assess a sample against a multivariate null distribution

### 2024-07-19 paper.qmd
fix typo

<IMAGES OF PROJECTED ELLIPSE>

@@

To define a measure of an interesting projection is to maximize the average Mahahlanobis distance [@mahalanobis] in the projection for a subset of points, $W$. The set of points could be chosen in different ways, but the default is those that are outside the specified ellipsoid in \pD{}. Alternatives could be to select a set of observations with the largest Mahalanobis distance, manually select observations or possibly a group of points identified via clustering of the extremes.

>>>>

@@

To define a measure of an interesting projection is to maximize the average Mahalanobis distance [@mahalanobis] in the projection for a subset of points, $W$. The set of points could be chosen in different ways, but the default is those that are outside the specified ellipsoid in \pD{}. Alternatives could be to select a set of observations with the largest Mahalanobis distance, manually select observations or possibly a group of points identified via clustering of the extremes.

### 2024-07-19 paper.tex
fix typo

To define a measure of an interesting projection is to maximize the
average Mahahlanobis distance \citep{mahalanobis} in the projection for
a subset of points, \(W\). The set of points could be chosen in
different ways, but the default is those that are outside the specified
ellipsoid in \pD{}. Alternatives could be to select a set of
observations with the largest Mahalanobis distance, manually select
observations or possibly a group of points identified via clustering of
the extremes.

>>>>

To define a measure of an interesting projection is to maximize the
average Mahalanobis distance \citep{mahalanobis} in the projection for a
subset of points, \(W\). The set of points could be chosen in different
ways, but the default is those that are outside the specified ellipsoid
in \pD{}. Alternatives could be to select a set of observations with the
largest Mahalanobis distance, manually select observations or possibly a
group of points identified via clustering of the extremes.
